\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Ernesto Casco} \\ \vspace{1pt}
    \small +52 722-616-9124 $|$ \href{mailto:ernesto.casco.velazquez@gmail.com}{\underline{ernesto.casco.velazquez@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ernesto-casco}{\underline{linkedin.com/in/ernesto-casco}} $|$
    \href{https://github.com/MrCasco}{\underline{github.com/MrCasco}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tecnologico de Monterrey}{Toluca, State of Mexico}
      {Bachelor in Computer Science}{Aug 2018 -- Dec 2022}
    \resumeItemListStart
        \resumeItem{GPA: 3.7/4.0}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{July 2023 -- Present}
      {Qualtrics}{Mexico City, MX}
      \resumeItemListStart
        \resumeItem{Write backend scripts in Golang to automate processes and improve service efficiency.}
        \resumeItem{Fix UI bugs using React, ensuring smooth and responsive user interfaces.}
        \resumeItem{Monitor and troubleshoot error codes and latency issues, ensuring minimal downtime and optimal performance.}
        \resumeItem{Collaborate in an AGILE environment, consistently delivering on sprint goals and improving development cycles.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineering Sr Analyst}{January 2022 -- July 2023}
      {PepsiCo}{Mexico City, MX}
      \resumeItemListStart
        \resumeItem{Developed 20+ screens from the front and back-end perspective to help managers see revenue and simulate price changes in products.}
        \resumeItem{Delivered 50+ tickets of high-quality and thoroughly-tested code in close time frames.}
        \resumeItem{Managed teams of 3+ developers to help them onboard and improve code quality.}
        \resumeItem{Provided insightful opinions with product teams to design platform architecture.}
      \resumeItemListEnd
    \resumeSubheading
      {Solutions Engineer}{January 2022 -- December 2022}
      {Facebook}{Mexico City, MX}
      \resumeItemListStart
        \resumeItem{Implemented a big data system using Python and SQL that tracked the most viewed, purchased, and added to cart products from advertisers' websites, increasing ROAS by 20\% for clients.}
        \resumeItem{Developed a logging system using Hack to store valuable data from the NFT-claiming funnel, impacting 10+ million people on Instagram.}
        \resumeItem{Collaborated with 5+ Facebook advertisers to reach business objectives, impacting \$100K+ in advertising spending for Meta.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Development Engineer Intern}{June 2021 -- August 2021}
      {Amazon}{Mexico City, MX}
      \resumeItemListStart
        \resumeItem{Developed back-end system with Python and AWS to filter 100,000+ Amazon products by drugs that needed prescriptions, ensuring compliance with federal regulations.}
        \resumeItem{Delivered analysis on why complying with federal drug regulations could save Amazon \$10,000+ USD in fees.}
      \resumeItemListEnd
    \resumeSubheading
      {Full-Stack Engineer}{June 2020 -- October 2021}
      {Ideen MX}{Mexico City, MX}
      \resumeItemListStart
        \resumeItem{Created the \emph{Kuida.io} app and web page that helps women track their menstrual cycle, find nearby doctors, and get healthy diets.}
        \resumeItem{Developed API with NodeJS to process payments via the Stripe API.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Makemore Drum Rhythms} $|$ \emph{Python, TensorFlow, Matplotlib, Numpy}}{January 2023 -- Current}
          \resumeItemListStart
            \resumeItem{Followed the course "Intro to Neural Networks" by Andrej Karpathy to create a neural network that takes drum tabs in JSON format as input and outputs similar rhythms using gradient descent.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{C-Minus Compiler} $|$ \emph{Python, C, Git}}{January 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{Developed a C-Minus compiler from the ground up using Python and Regex.}
            \resumeItem{Published the compiler within the Git network, helping 10+ students from different schools across the country.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, C++, Hack, PHP, SQL, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, Flutter, VueJS} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, AWS, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, PyTorch, TensorFlow}
    }}
 \end{itemize}

\end{document}
